---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, fig.width = 7,
               fig.path = "man/figures/canva-")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5", cache = TRUE)
```

Table of Contents
=================
  * [Main page](README.md#comprehensive-list-of-color-palettes-in-r)
  * [Blogposts and other resources](README.md#blogposts-and-other-resources)
  * [Generative packages](README.md#generative-packages)
  * [Honorable mentions](README.md#honorable-mentions)
  * [Palettes sorted by Package (alphabetically)](README.md#palettes-sorted-by-package-alphabetically)
    * [Sequential color palettes](#sequential-color-palettes)
    * [Diverging color palettes](#diverging-color-palettes)
    * [Qualitative color palettes](#qualitative-color-palettes)
    * [Canva palettes](canva.md)
    * [Palettetown palettes](palettetown.md)
  * [News](NEWS.md)

### Canva palattes

All of these palettes are avaliable with `ggthemes` package `ggthemes::canva_palettes` and `ggthemes::canva_pal()`.

```{r canva1, fig.height=31}
names <- names(ggthemes::canva_palettes)

pals::pal.bands(
  ggthemes::canva_palettes[[1]],
  ggthemes::canva_palettes[[2]],
  ggthemes::canva_palettes[[3]],
  ggthemes::canva_palettes[[4]],
  ggthemes::canva_palettes[[5]],
  ggthemes::canva_palettes[[6]],
  ggthemes::canva_palettes[[7]],
  ggthemes::canva_palettes[[8]],
  ggthemes::canva_palettes[[9]],
  ggthemes::canva_palettes[[10]],
  ggthemes::canva_palettes[[11]],
  ggthemes::canva_palettes[[12]],
  ggthemes::canva_palettes[[13]],
  ggthemes::canva_palettes[[14]],
  ggthemes::canva_palettes[[15]],
  ggthemes::canva_palettes[[16]],
  ggthemes::canva_palettes[[17]],
  ggthemes::canva_palettes[[18]],
  ggthemes::canva_palettes[[19]],
  ggthemes::canva_palettes[[20]],
  ggthemes::canva_palettes[[21]],
  ggthemes::canva_palettes[[22]],
  ggthemes::canva_palettes[[23]],
  ggthemes::canva_palettes[[24]],
  ggthemes::canva_palettes[[25]],
  ggthemes::canva_palettes[[26]],
  ggthemes::canva_palettes[[27]],
  ggthemes::canva_palettes[[28]],
  ggthemes::canva_palettes[[29]],
  ggthemes::canva_palettes[[30]],
  labels = names[1:30],
  main = "Canva 1-30"
)
```

```{r canva2, fig.height=31}
names <- names(ggthemes::canva_palettes)

pals::pal.bands(
  ggthemes::canva_palettes[[31]],
  ggthemes::canva_palettes[[32]],
  ggthemes::canva_palettes[[33]],
  ggthemes::canva_palettes[[34]],
  ggthemes::canva_palettes[[35]],
  ggthemes::canva_palettes[[36]],
  ggthemes::canva_palettes[[37]],
  ggthemes::canva_palettes[[38]],
  ggthemes::canva_palettes[[39]],
  ggthemes::canva_palettes[[40]],
  ggthemes::canva_palettes[[41]],
  ggthemes::canva_palettes[[42]],
  ggthemes::canva_palettes[[43]],
  ggthemes::canva_palettes[[44]],
  ggthemes::canva_palettes[[45]],
  ggthemes::canva_palettes[[46]],
  ggthemes::canva_palettes[[47]],
  ggthemes::canva_palettes[[48]],
  ggthemes::canva_palettes[[49]],
  ggthemes::canva_palettes[[50]],
  ggthemes::canva_palettes[[51]],
  ggthemes::canva_palettes[[52]],
  ggthemes::canva_palettes[[53]],
  ggthemes::canva_palettes[[54]],
  ggthemes::canva_palettes[[55]],
  ggthemes::canva_palettes[[56]],
  ggthemes::canva_palettes[[57]],
  ggthemes::canva_palettes[[58]],
  ggthemes::canva_palettes[[59]],
  ggthemes::canva_palettes[[60]],
  labels = names[31:60],
  main = "Canva 31-60"
)
```

```{r canva3, fig.height=31}
names <- names(ggthemes::canva_palettes)

pals::pal.bands(
  ggthemes::canva_palettes[[61]],
  ggthemes::canva_palettes[[62]],
  ggthemes::canva_palettes[[63]],
  ggthemes::canva_palettes[[64]],
  ggthemes::canva_palettes[[65]],
  ggthemes::canva_palettes[[66]],
  ggthemes::canva_palettes[[67]],
  ggthemes::canva_palettes[[68]],
  ggthemes::canva_palettes[[69]],
  ggthemes::canva_palettes[[70]],
  ggthemes::canva_palettes[[71]],
  ggthemes::canva_palettes[[72]],
  ggthemes::canva_palettes[[73]],
  ggthemes::canva_palettes[[74]],
  ggthemes::canva_palettes[[75]],
  ggthemes::canva_palettes[[76]],
  ggthemes::canva_palettes[[77]],
  ggthemes::canva_palettes[[78]],
  ggthemes::canva_palettes[[79]],
  ggthemes::canva_palettes[[80]],
  ggthemes::canva_palettes[[81]],
  ggthemes::canva_palettes[[82]],
  ggthemes::canva_palettes[[83]],
  ggthemes::canva_palettes[[84]],
  ggthemes::canva_palettes[[85]],
  ggthemes::canva_palettes[[86]],
  ggthemes::canva_palettes[[87]],
  ggthemes::canva_palettes[[88]],
  ggthemes::canva_palettes[[89]],
  ggthemes::canva_palettes[[90]],
  labels = names[61:90],
  main = "Canva 61-90"
)
```

```{r canva4, fig.height=31}
names <- names(ggthemes::canva_palettes)

pals::pal.bands(
  ggthemes::canva_palettes[[91]],
  ggthemes::canva_palettes[[92]],
  ggthemes::canva_palettes[[93]],
  ggthemes::canva_palettes[[94]],
  ggthemes::canva_palettes[[95]],
  ggthemes::canva_palettes[[96]],
  ggthemes::canva_palettes[[97]],
  ggthemes::canva_palettes[[98]],
  ggthemes::canva_palettes[[99]],
  ggthemes::canva_palettes[[100]],
  ggthemes::canva_palettes[[101]],
  ggthemes::canva_palettes[[102]],
  ggthemes::canva_palettes[[103]],
  ggthemes::canva_palettes[[104]],
  ggthemes::canva_palettes[[105]],
  ggthemes::canva_palettes[[106]],
  ggthemes::canva_palettes[[107]],
  ggthemes::canva_palettes[[108]],
  ggthemes::canva_palettes[[109]],
  ggthemes::canva_palettes[[110]],
  ggthemes::canva_palettes[[111]],
  ggthemes::canva_palettes[[112]],
  ggthemes::canva_palettes[[113]],
  ggthemes::canva_palettes[[114]],
  ggthemes::canva_palettes[[115]],
  ggthemes::canva_palettes[[116]],
  ggthemes::canva_palettes[[117]],
  ggthemes::canva_palettes[[118]],
  ggthemes::canva_palettes[[119]],
  ggthemes::canva_palettes[[120]],
  labels = names[91:120],
  main = "Canva 91-120"
)
```

```{r canva5, fig.height=31}
names <- names(ggthemes::canva_palettes)

pals::pal.bands(
  ggthemes::canva_palettes[[121]],
  ggthemes::canva_palettes[[122]],
  ggthemes::canva_palettes[[123]],
  ggthemes::canva_palettes[[124]],
  ggthemes::canva_palettes[[125]],
  ggthemes::canva_palettes[[126]],
  ggthemes::canva_palettes[[127]],
  ggthemes::canva_palettes[[128]],
  ggthemes::canva_palettes[[129]],
  ggthemes::canva_palettes[[130]],
  ggthemes::canva_palettes[[131]],
  ggthemes::canva_palettes[[132]],
  ggthemes::canva_palettes[[133]],
  ggthemes::canva_palettes[[134]],
  ggthemes::canva_palettes[[135]],
  ggthemes::canva_palettes[[136]],
  ggthemes::canva_palettes[[137]],
  ggthemes::canva_palettes[[138]],
  ggthemes::canva_palettes[[139]],
  ggthemes::canva_palettes[[140]],
  ggthemes::canva_palettes[[141]],
  ggthemes::canva_palettes[[142]],
  ggthemes::canva_palettes[[143]],
  ggthemes::canva_palettes[[144]],
  ggthemes::canva_palettes[[145]],
  ggthemes::canva_palettes[[146]],
  ggthemes::canva_palettes[[147]],
  ggthemes::canva_palettes[[148]],
  ggthemes::canva_palettes[[149]],
  ggthemes::canva_palettes[[150]],
  labels = names[121:150],
  main = "Canva 121-150"
)
```