---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

## Palettes sorted by type (Sequential/Diverging/Qualitative)

Table of Contents
=================
  * [Main page](README.md#comprehensive-list-of-color-palettes-in-r)
  * [Blogposts and other resources](README.md#blogposts-and-other-resources)
  * [Color manipulation packages](README.md#color-manipulation-packages)
  * [Generative packages](README.md#generative-packages)
  * [Perception of color palettes](README.md#perception-of-color-palettes)
    * [Printing in black and white](README.md#printing-in-black-and-white)
    * [Color blindness](README.md#color-blindness)
  * [Honorable mentions](README.md#honorable-mentions)
  * [Palettes sorted by Package (alphabetically)](README.md#palettes-sorted-by-package-alphabetically)
    * [Sequential color palettes](#sequential-color-palettes)
    * [Diverging color palettes](#diverging-color-palettes)
    * [Qualitative color palettes](#qualitative-color-palettes)
    * [Canva palettes](canva.md)
    * [Palettetown palettes](palettetown.md)
  * [News](NEWS.md)

### Sequential color palettes

```{r}
#| results: asis
#| warning: false
source("palette_plotter.R")
fs::dir_create("palette_images")

pals <- paletteer::palettes_d
pals <- pals[names(pals) != "palettetown"]

for (i in seq_along(pals)) {
  pal_package <- names(pals)[i] 
  pal <- pals[[i]]

info <- paletteer::palettes_d_names |>
  filter(package == pal_package) |>
  arrange(palette) |>
  filter(!novelty)

  if (nrow(info) > 0) {

    pal_names <- info$palette
    make_plot(pal[pal_names], paste0("nonnovel", "-", pal_package))
  }
}
```

```{r}
#| results: asis
#| warning: false
pkg_data <- paletteer::palettes_d_names |>
  filter(!novelty) |>
  distinct(package) |>
  left_join(paletteer::paletteer_packages, by = c("package" = "Name")) |>
  mutate(
    github_install = if_else(
      is.na(github_ver),
      "",
      glue::glue("# Developmental version\npak::pak(\"{Github}\")")
    ),
    cran_install = if_else(
      CRAN,
      glue::glue("\n\n# CRAN version\ninstall.packages(\"{package}\")\n\n"),
      ""
    )
  )

glue::glue_data(
  pkg_data,
  "
### [[package]]

\`\`\`r
[[github_install]]
[[cran_install]]
\`\`\`

![](palette_images/nonnovel-[[package]].png)

",
  .open = "[[",
  .close = "]]"
)
```
