---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, cache = TRUE, fig.width = 7,
               fig.path = "man/figures/README-")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

# Comprehensive list of color palettes in r

The goal of this repository is to have a one stop destination for anyone looking for a color palette to use in r. If you would like to help/contribute please feel free post an issue, PR or send a email to [emilhhvitfeldt@gmail.com](mailto:emilhhvitfeldt@gmail.com).

----- **Attention** -----  
As this project is still in its early days I especially appreciate feedback on packages I have overlooked.  

Further down the page is all the palettes available in the R ecosystem order alphabetically by package name. A list of palettes ordered by type can be found here [Type sorted palettes](type-sorted-palettes.md) to shorten the length of this page.

Table of Contents
=================
  * [Main page](#comprehensive-list-of-color-palettes-in-r)
  * [Blogposts and other resources](#blogposts-and-other-resources)
  * [Generative packages](#generative-packages)
  * [Perception of color palettes](#perception-of-color-palettes)
    * [Printing in black and white](#printing-in-black-and-white)
    * [Color blindness](#color-blindness)
  * [Honorable mentions](#honorable-mentions)
  * [Palettes sorted by Package (alphabetically)](#palettes-sorted-by-package-alphabetically)
    * [Sequential color palettes](type-sorted-palettes.md#sequential-color-palettes)
    * [Diverging color palettes](type-sorted-palettes.md#diverging-color-palettes)
    * [Qualitative color palettes](type-sorted-palettes.md#qualitative-color-palettes)
    * [Canva palettes](canva.md)
  * [News](NEWS.md)

## Blogposts and other resources

Here is a collection of material on the use and creation of color palettes in r.

- [Creating corporate colour palettes for ggplot2](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2)
- [Make your own color palettes with paletti](https://edwinth.github.io/blog/paletti/)
- [How to create a color palette in R with more than 15 colors with ggplot2 ](https://github.com/duttashi/visualize/issues/19)
- [Generating a Custom Color Palette Function in R](https://quantdev.ssri.psu.edu/tutorials/generating-custom-color-palette-function-r)
- [How to build a color palette from any image with R and k-means algo](http://www.milanor.net/blog/build-color-palette-from-image-with-paletter/)
- [How to Read, Inspect, and Manipulate Color Swatch Files](https://github.com/hrbrmstr/swatches)
- [extract palettes from images and text](https://github.com/EmilHvitfeldt/quickpalette)

## Generative packages

The purpose of this project is to showcase the palettes already available in R (packages). However sometimes you have to resort to make one yourself. When that is the case the following packages aides in creating.

- [AndreaCirilloAC/paletter](https://github.com/AndreaCirilloAC/paletter)
- [jolars/qualpalr](https://github.com/jolars/qualpalr)
- [ronammar/randomcoloR](https://github.com/ronammar/randomcoloR)
- [johnbaums/hues](https://github.com/johnbaums/hues)
- [ColorPalette](https://cran.r-project.org/web/packages/ColorPalette/index.html)
- [oaColors](https://cran.rstudio.com/web/packages/oaColors/index.html)
- [earthtones](https://cran.r-project.org/web/packages/earthtones/index.html)
- [leeper/colourlovers](https://github.com/leeper/colourlovers)

When creating color palettes certain website have also provided valuable

- [paletton](http://paletton.com/)
- [Data color picker](https://learnui.design/tools/data-color-picker.html)
- [i want hue](http://tools.medialab.sciences-po.fr/iwanthue/)

## Perception of color palettes

Selecting a color palette requires a number of different considerations. Within these considerations is

- the palette retains its integrity when printed in black and white
- people with colorblindness are able to understand it

In the following I have outlined a couple of those problems

### Printing in black and white

While most of the palettes presented here contains a wide variety of colors. While that is compelling, you need to remember that your product might be printed in black and white one day, and you should pick a palette that allows for interpretation if that is the case.  

first example is the `rainbow` palette from the `grDevices` package with its colorful display. However as we see here would it be horrible if used for black and white printing since different colors are mapped to the same shade of grey.

```{r, fig.height=3}
pal <- rainbow(32)
pals::pal.bands(
  pal,
  colorspace::desaturate(pal),
  labels = c("Normal", "desaturated"),
  main = "Normal rainbow palette"
)
```

A related problem happens with the standard color palette used in `ggplot2` since that color is picked to have constant chroma and luminance thus yielding the same shade of grey when desaturated.

```{r fig.height=3}
pal <- scales::hue_pal()(256)
pals::pal.bands(
  pal,
  colorspace::desaturate(pal),
  labels = c("Normal", "desaturated"),
  main = "Standard color palette for ggplot2"
)
```

One of the continuous palette that satisfy this criteria is the well known `viridis` palettes.

```{r fig.height=3}
pal <- viridis::inferno(32)
pals::pal.bands(
  pal,
  colorspace::desaturate(pal),
  labels = c("Normal", "desaturated"),
  main = "viridis::inferno"
)
```

To test if the palette you want to use will be distorted when in black and white, use the `colorspace::desaturate()` to desaturate it. 

### Color blindness

Another thing you have to take into consideration when picking a palette is how it would be viewed by a person who is [color blind](https://en.wikipedia.org/wiki/Color_blindness). To visualize the effect of color blindness on our palettes we will turn to two packages. The `dichromat` package can simulate color blindness on individual color and then also entire palettes like so in this `rainbow` palette:

```{r}
pal <- rainbow(32)
pals::pal.bands(
  pal,
  dichromat::dichromat(pal, type = "deutan"),
  dichromat::dichromat(pal, type = "protan"),
  dichromat::dichromat(pal, type = "tritan"),
  labels = c("Normal", "deuteranopia", "protanopia", "tritanopia"),
  main = "The effect of color blindness on the rainbow"
)
```

Another package that can provide helpful is the amazing [colorblindr](https://github.com/clauswilke/colorblindr) package that is able to simulate color blindness to `ggplot` objects them self.

## Honorable mentions

Due to the somehow vague notion of "color palette" have I decided to exclude certain kinds of packages from the main gallery. [Generative package](#generative-packages) have been discussed earlier. 

### cpt-city

The amazing [cpt-city](http://soliton.vm.bytemark.co.uk/pub/cpt-city/index.html) is a wonderful project of creating an archive of color palettes to be used in cartography, technical illustration and design. Due to the immense size (7140) I have decided to refer to it instead of re-illustration them in this repository. If any of the palettes found here are for your liking they can be accessed in R using the following [package](https://cran.r-project.org/web/packages/cptcity/index.html):

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("cptcity")
```

### sport colors

Many of the palettes in sports related palettes have a very limited number of colors (often only 2 colors). This leads to quite low usability outside of the special area of sports analytic.

- [colorr](https://cran.r-project.org/web/packages/colorr/index.html)
Color palettes for EPL, MLB, NBA, NHL, and NFL teams.

- [beanumber/teamcolors](https://github.com/beanumber/teamcolors)
An R package providing color palettes for pro sports teams.

### Canva palettes

The `ggthemes` package include the 150 four-color palettes from the [canva.com](canva.com). Doe to the size and limited number of colors in the palettes these palettes will be featured on their own page and only once.

- [Canva colors](canvas.md)

## Palettes sorted by Package (alphabetically)

```{r awtools, fig.height=6}
pals::pal.bands(
  awtools::a_palette,
  awtools::a_spalette,
  awtools::mpalette,
  awtools::ppalette,
  awtools::spalette,
  labels = c("a_palette", "a_spalette", "mpalette", "ppalette", 
             "spalette"),
  main = "awtools"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("awhstin/awtools")
```

```{r dichromat, fig.height=18}
pals::pal.bands(
  dichromat::colorschemes[[1]],
  dichromat::colorschemes[[2]],
  dichromat::colorschemes[[3]],
  dichromat::colorschemes[[4]],
  dichromat::colorschemes[[5]],
  dichromat::colorschemes[[6]],
  dichromat::colorschemes[[7]],
  dichromat::colorschemes[[8]],
  dichromat::colorschemes[[9]],
  dichromat::colorschemes[[10]],
  dichromat::colorschemes[[11]],
  dichromat::colorschemes[[12]],
  dichromat::colorschemes[[13]],
  dichromat::colorschemes[[14]],
  dichromat::colorschemes[[15]],
  dichromat::colorschemes[[16]],
  dichromat::colorschemes[[17]],
  labels = names(dichromat::colorschemes),
  main = "dichromat"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("dichromat")
```


```{r dutchmasters, fig.height=7}
pals::pal.bands(
  unname(dutchmasters::dutchmasters[[1]]),
  unname(dutchmasters::dutchmasters[[2]]),
  unname(dutchmasters::dutchmasters[[3]]),
  unname(dutchmasters::dutchmasters[[4]]),
  unname(dutchmasters::dutchmasters[[5]]),
  unname(dutchmasters::dutchmasters[[6]]),
  labels = names(dutchmasters::dutchmasters),
  main = "dutchmasters"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("EdwinTh/dutchmasters")
```

```{r ggsci, fig.height=43}
pals::pal.bands(
  ggsci::pal_npg("nrc")(10),
  ggsci::pal_aaas("default")(10),
  ggsci::pal_nejm("default")(8),
  ggsci::pal_lancet("lanonc")(9),
  ggsci::pal_jama("default")(7),
  ggsci::pal_jco("default")(10),
  ggsci::pal_ucscgb("default")(26),
  ggsci::pal_d3("category10")(10),
  ggsci::pal_d3("category20")(20),
  ggsci::pal_d3("category20b")(20),
  ggsci::pal_d3("category20c")(20),
  ggsci::pal_locuszoom("default")(7),
  ggsci::pal_igv("default")(51),
  ggsci::pal_igv("alternating")(2),
  ggsci::pal_uchicago("default")(9),
  ggsci::pal_uchicago("light")(9),
  ggsci::pal_uchicago("dark")(9),
  ggsci::pal_startrek("uniform")(7),
  ggsci::pal_tron("legacy")(7),
  ggsci::pal_futurama("planetexpress")(12),
  ggsci::pal_rickandmorty("schwifty")(12),
  ggsci::pal_simpsons("springfield")(16),
  ggsci::pal_gsea("default")(12),
  ggsci::pal_material("red")(10),
  ggsci::pal_material("pink")(10),
  ggsci::pal_material("purple")(10),
  ggsci::pal_material("deep-purple")(10),
  ggsci::pal_material("indigo")(10),
  ggsci::pal_material("blue")(10),
  ggsci::pal_material("light-blue")(10),
  ggsci::pal_material("cyan")(10),
  ggsci::pal_material("teal")(10),
  ggsci::pal_material("green")(10),
  ggsci::pal_material("light-green")(10),
  ggsci::pal_material("lime")(10),
  ggsci::pal_material("yellow")(10),
  ggsci::pal_material("amber")(10),
  ggsci::pal_material("orange")(10),
  ggsci::pal_material("deep-orange")(10),
  ggsci::pal_material("brown")(10),
  ggsci::pal_material("grey")(10),
  ggsci::pal_material("blue-grey")(10),
  labels = c("npg", "aaas", "nejm", "lancet", "jama", "jco", "ucscgb", 
             "d3-category10", "d3-category20", "d3-category20b", 
             "d3-category20c", "locuszoom", "igv-default", "igv-alternative",
             "uchicago-default", "uchicago-light", "uchicago-dark", "startrek",
             "tron", "futurama", "rickandmorty", "simpsoms", "gsea", 
             "material-red", "material-pink", "material-purple", 
             "material-deep-purple", "material-indigo", "material-blue",
             "material-light-blue", "material-cyan", "material-teal", 
             "material-green", "material-light-green", "material-lime",
             "material-yellow", "material-amber", "material-orange",
             "material-deep-orange", "material-brown", "material-grey",
             "material-blue-grey"),
  main = "ggsci"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r ggpomological, fig.height=3}
pals::pal.bands(
  ggpomological:::pomological_palette,
  unlist(ggpomological:::pomological_base), 
  labels = c("pomological_palette", "pomological_base"),
  main = "ggpomological",
  show.names = FALSE
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("gadenbuie/ggpomological")
```

```{r ggthemes, fig.height=25}
pals::pal.bands(
  ggthemes::calc_pal()(12),
  ggthemes::colorblind_pal()(8),
  ggthemes::economist_pal()(9),
  ggthemes::excel_pal(palette = "old")(7),
  ggthemes::excel_pal(palette = "fill")(7),
  ggthemes::excel_pal(palette = "new")(10),
  ggthemes::few_pal(palette = "medium")(7),
  ggthemes::few_pal(palette = "dark")(7),
  ggthemes::few_pal(palette = "light")(7),
  ggthemes::fivethirtyeight_pal()(3),
  ggthemes::gdocs_pal()(20),
  ggthemes::hc_pal(palette = "default")(10),
  ggthemes::hc_pal(palette = "darkunica")(11),
  ggthemes::ptol_pal()(12),
  ggthemes::solarized_pal()(8),
  ggthemes::stata_pal(scheme = "s2color")(15),
  ggthemes::stata_pal(scheme = "s1rcolor")(15),
  ggthemes::stata_pal(scheme = "s1color")(15),
  ggthemes::stata_pal(scheme = "mono")(15),
  ggthemes::wsj_pal(palette = "rgby")(4),
  ggthemes::wsj_pal(palette = "red_green")(2),
  ggthemes::wsj_pal(palette = "black_green")(4),
  ggthemes::wsj_pal(palette = "dem_rep")(3),
  ggthemes::wsj_pal(palette = "colors6")(6),
  labels = c("calc", "colorblind", "economist", "excel-old", "excel-fill",
             "excel-new", "few-medium", "few-dark", "few-light", 
             "fivethirtyeight", "gdocs", "hc-default", "hc-darkunica",
             "ptol", "solarized", "stata-s2color", "stata-s1rcolor",
             "stata-s1color", "stata-mono", "wsj-rgby", "wsj-red_green",
             "wsj-black_green", "wsj-dem_rep", "wjs-colors6"),
  main = "ggthemes"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jrnold/ggthemes")
# CRAN version
install.packages("ggthemes")
```

```{r ggthemestableau, fig.height=47}
names <- c(names(ggthemes::ggthemes_data$tableau$colors),
        "tableau10", "tableau10light", 
        "purplegray6", "bluered6", "greenorange6")
namesdiv <- names(ggthemes::ggthemes_data[["tableau"]][["diverging"]])
namesseq <- names(ggthemes::ggthemes_data$tableau$sequential)

pals::pal.bands(
  ggthemes::tableau_color_pal(palette = names[1])(20),
  ggthemes::tableau_color_pal(palette = names[2])(10),
  ggthemes::tableau_color_pal(palette = names[3])(5),
  ggthemes::tableau_color_pal(palette = names[4])(10),
  ggthemes::tableau_color_pal(palette = names[5])(9),
  ggthemes::tableau_color_pal(palette = names[6])(12),
  ggthemes::tableau_color_pal(palette = names[7])(12),
  ggthemes::tableau_color_pal(palette = names[8])(12),
  ggthemes::tableau_color_pal(palette = names[9])(20),
  ggthemes::tableau_color_pal(palette = names[10])(10),
  ggthemes::tableau_color_pal(palette = names[11])(10),
  ggthemes::tableau_color_pal(palette = names[12])(6),
  ggthemes::tableau_color_pal(palette = names[13])(6),
  ggthemes::tableau_color_pal(palette = names[14])(6),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[1])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[2])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[3])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[4])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[5])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[6])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[7])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[8])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[9])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[10])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[11])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[12])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[13])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[14])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[15])((1:100)/100),
  ggthemes::tableau_div_gradient_pal(palette = namesdiv[16])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[1])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[2])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[3])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[4])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[5])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[6])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[7])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[8])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[9])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[10])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[11])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[12])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[13])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[14])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[15])((1:100)/100),
  ggthemes::tableau_seq_gradient_pal(palette = namesseq[16])((1:100)/100),
  labels = c(names, namesdiv, namesseq),
  main = "ggthemes (tableau)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jrnold/ggthemes")
# CRAN version
install.packages("ggthemes")
```

```{r ghibli, fig.height=28}
pals::pal.bands(
  ghibli::ghibli_palettes[[1]],
  ghibli::ghibli_palettes[[2]],
  ghibli::ghibli_palettes[[3]],
  ghibli::ghibli_palettes[[4]],
  ghibli::ghibli_palettes[[5]],
  ghibli::ghibli_palettes[[6]],
  ghibli::ghibli_palettes[[7]],
  ghibli::ghibli_palettes[[8]],
  ghibli::ghibli_palettes[[9]],
  ghibli::ghibli_palettes[[10]],
  ghibli::ghibli_palettes[[11]],
  ghibli::ghibli_palettes[[12]],
  ghibli::ghibli_palettes[[13]],
  ghibli::ghibli_palettes[[14]],
  ghibli::ghibli_palettes[[15]],
  ghibli::ghibli_palettes[[16]],
  ghibli::ghibli_palettes[[17]],
  ghibli::ghibli_palettes[[18]],
  ghibli::ghibli_palettes[[19]],
  ghibli::ghibli_palettes[[20]],
  ghibli::ghibli_palettes[[21]],
  ghibli::ghibli_palettes[[22]],
  ghibli::ghibli_palettes[[23]],
  ghibli::ghibli_palettes[[24]],
  ghibli::ghibli_palettes[[25]],
  ghibli::ghibli_palettes[[26]],
  ghibli::ghibli_palettes[[27]],
  labels = names(ghibli::ghibli_palettes),
  main = "ghibli"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ewenme/ghibli")
# CRAN version
install.packages("ghibli")
```

```{r grDevices, fig.height=7}
pals::pal.bands(
  grDevices::blues9,
  rainbow(100),
  heat.colors(100),
  terrain.colors(100),
  topo.colors(100),
  cm.colors(100),
  labels = c("blues9", "rainbow", "heat.colors", "terrain.colors",
             "topo.colors", "cm.colors"),
  main = "grDevices"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("grDevices")
```

```{r nord, fig.height=17}
pals::pal.bands(
  nord::nord_palettes[[1]],
  nord::nord_palettes[[2]],
  nord::nord_palettes[[3]],
  nord::nord_palettes[[4]],
  nord::nord_palettes[[5]],
  nord::nord_palettes[[6]],
  nord::nord_palettes[[7]],
  nord::nord_palettes[[8]],
  nord::nord_palettes[[9]],
  nord::nord_palettes[[10]],
  nord::nord_palettes[[11]],
  nord::nord_palettes[[12]],
  nord::nord_palettes[[13]],
  nord::nord_palettes[[14]],
  nord::nord_palettes[[15]],
  nord::nord_palettes[[16]],
  labels = names(nord::nord_palettes),
  main = "nord"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r ochRe, fig.height=17}
pals::pal.bands(
  unname(ochRe::ochre_palettes[[1]]),
  unname(ochRe::ochre_palettes[[2]]),
  unname(ochRe::ochre_palettes[[3]]),
  unname(ochRe::ochre_palettes[[4]]),
  unname(ochRe::ochre_palettes[[5]]),
  unname(ochRe::ochre_palettes[[6]]),
  unname(ochRe::ochre_palettes[[7]]),
  unname(ochRe::ochre_palettes[[8]]),
  unname(ochRe::ochre_palettes[[9]]),
  unname(ochRe::ochre_palettes[[10]]),
  unname(ochRe::ochre_palettes[[11]]),
  unname(ochRe::ochre_palettes[[12]]),
  unname(ochRe::ochre_palettes[[13]]),
  unname(ochRe::ochre_palettes[[14]]),
  unname(ochRe::ochre_palettes[[15]]),
  unname(ochRe::ochre_palettes[[16]]),
  labels = names(ochRe::ochre_palettes),
  main = "ochRe"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ropenscilabs/ochRe")
# CRAN version
install.packages("ochRe")
```

```{r oompaBase, fig.height=9}
pals::pal.bands(
  oompaBase::redscale(100),
  oompaBase::greenscale(100),
  oompaBase::bluescale(100),
  oompaBase::blueyellow(100),
  oompaBase::cyanyellow(100),
  oompaBase::redgreen(100),
  oompaBase::jetColors(100),
  oompaBase::greyscale(100),
  labels = c("redscale", "greenscale", "bluescale", "blueyellow", "cyanyellow",
             "redgreen", "jetColors", "greyscale"),
  main = "oompaBase"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("oompaBase")
```

```{r palettetown, fig.height=11}
ids <- c(6, 17, 114, 137, 156, 191, 193, 283, 311, 318)
names <- c("charizard", "pidgeotto", "tangela", "porygon", "quilava", 
           "sunkern", "yanma", "surskit", "plusle", "carvanha")

pals::pal.bands(
  palettetown::ichooseyou(ids[1]),
  palettetown::ichooseyou(ids[2]),
  palettetown::ichooseyou(ids[3]),
  palettetown::ichooseyou(ids[4]),
  palettetown::ichooseyou(ids[5]),
  palettetown::ichooseyou(ids[6]),
  palettetown::ichooseyou(ids[7]),
  palettetown::ichooseyou(ids[8]),
  palettetown::ichooseyou(ids[9]),
  palettetown::ichooseyou(ids[10]),
  labels = stringr::str_c(ids, " - ", names),
  main = "palettetown"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("timcdlucas/palettetown")
# CRAN version
install.packages("palettetown")
```

```{r palr, fig.height=5}
pals::pal.bands(
  palr::bathyDeepPal(100),
  palr::chlPal(100),
  palr::icePal(100),
  palr::sstPal(100),
  labels = c("bathyDeepPal", "chlPal", "icePal", "sstPal"),
  main = "palr"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("AustralianAntarcticDivision/palr")
# CRAN version
install.packages("palr")
```

```{r palsdiscrete, fig.height=9}
pals::pal.bands(
  pals::alphabet(), 
  pals::alphabet2(), 
  pals::glasbey(), 
  pals::kelly(),
  pals::polychrome(), 
  pals::stepped(), 
  pals::tol(), 
  pals::watlington(), 
  labels = c('alphabet','alphabet2', 'glasbey','kelly','polychrome', 'stepped',
             'tol', 'watlington'), 
  main = "pals (Discrete)",
  show.names = FALSE
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palscontinuous, fig.height=8}
pals::pal.bands(
  pals::coolwarm,
  pals::warmcool,
  pals::cubehelix,
  pals::gnuplot,
  pals::jet,
  pals::parula,
  pals::tol.rainbow,
  labels = c("coolwarm", "warmcool", "cubehelix", "gnuplot", "jet", "parula",
             "tol.rainbow"),
  main = "pals (Continuous)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsniccoli, fig.height=6}
pals::pal.bands(
  pals::cubicyf,
  pals::cubicl,
  pals::isol,
  pals::linearl,
  pals::linearlhot,
  labels = c("cubicyf", "cubicl", "isol", "linearl", "linearlhot"),
  main = "pals (Niccoli)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsocean, fig.height=19}
pals::pal.bands(
  pals::ocean.thermal, 
  pals::ocean.haline, 
  pals::ocean.solar, 
  pals::ocean.ice, 
  pals::ocean.gray,
  pals::ocean.oxy, 
  pals::ocean.deep, 
  pals::ocean.dense, 
  pals::ocean.algae, 
  pals::ocean.matter,
  pals::ocean.turbid, 
  pals::ocean.speed, 
  pals::ocean.amp, 
  pals::ocean.tempo, 
  pals::ocean.phase,
  pals::ocean.balance, 
  pals::ocean.delta, 
  pals::ocean.curl, 
  labels = c("thermal", "haline", "solar", "ice", "gray", "oxy", "deep", "dense",
             "algae", "matter", "turbid", "speed", "amp", "tempo", "phase",
             "balance", "delta", "curl"),
  main = "pals (Ocean)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovosi, message=FALSE, fig.height=30}
library(pals)
pal.bands(
  kovesi.cyclic_grey_15_85_c0, kovesi.cyclic_grey_15_85_c0_s25,
  kovesi.cyclic_mrybm_35_75_c68, kovesi.cyclic_mrybm_35_75_c68_s25,
  kovesi.cyclic_mygbm_30_95_c78, kovesi.cyclic_mygbm_30_95_c78_s25,
  kovesi.cyclic_wrwbw_40_90_c42, kovesi.cyclic_wrwbw_40_90_c42_s25,
  kovesi.diverging_isoluminant_cjm_75_c23, kovesi.diverging_isoluminant_cjm_75_c24,
  kovesi.diverging_isoluminant_cjo_70_c25, kovesi.diverging_linear_bjr_30_55_c53,
  kovesi.diverging_linear_bjy_30_90_c45, kovesi.diverging_rainbow_bgymr_45_85_c67,
  kovesi.diverging_bkr_55_10_c35, kovesi.diverging_bky_60_10_c30,
  kovesi.diverging_bwr_40_95_c42, kovesi.diverging_bwr_55_98_c37,
  kovesi.diverging_cwm_80_100_c22, kovesi.diverging_gkr_60_10_c40,
  kovesi.diverging_gwr_55_95_c38, kovesi.diverging_gwv_55_95_c39,
  kovesi.isoluminant_cgo_70_c39, kovesi.isoluminant_cgo_80_c38,
  kovesi.isoluminant_cm_70_c39, kovesi.rainbow_bgyr_35_85_c72, kovesi.rainbow_bgyr_35_85_c73,
  kovesi.rainbow_bgyrm_35_85_c69, kovesi.rainbow_bgyrm_35_85_c71,
  main = "pals (Kovesi)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovisilinear, fig.height=22}
library(pals)
pal.bands(
  kovesi.linear_bgy_10_95_c74, kovesi.linear_bgyw_15_100_c67, 
  kovesi.linear_bgyw_15_100_c68, kovesi.linear_blue_5_95_c73, 
  kovesi.linear_blue_95_50_c20, kovesi.linear_bmw_5_95_c86,
  kovesi.linear_bmw_5_95_c89, kovesi.linear_bmy_10_95_c71,
  kovesi.linear_bmy_10_95_c78, kovesi.linear_gow_60_85_c27,
  kovesi.linear_gow_65_90_c35, kovesi.linear_green_5_95_c69, 
  kovesi.linear_grey_0_100_c0, kovesi.linear_grey_10_95_c0,
  kovesi.linear_kry_5_95_c72, kovesi.linear_kry_5_98_c75,
  kovesi.linear_kryw_5_100_c64, kovesi.linear_kryw_5_100_c67,
  kovesi.linear_ternary_blue_0_44_c57, kovesi.linear_ternary_green_0_46_c42,
  kovesi.linear_ternary_red_0_50_c52,
  main = "pals (Kovesi linear)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r Polychrome, fig.height=8}
pals::pal.bands(
  Polychrome::alphabet.colors(),
  Polychrome::dark.colors(),
  Polychrome::glasbey.colors(),
  Polychrome::green.armytage.colors(),
  Polychrome::kelly.colors(),
  Polychrome::light.colors(),
  Polychrome::palette36.colors(),
  show.names = FALSE,
  labels = c("alphabet", "dark", "glasbey", "green armytage", "kelly", "light",
             "palette36"),
  main = "Polychrome"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Polychrome")
```

```{r quickpalette, fig.height=6}
pals::pal.bands(
  quickpalette::qp_art[[1]],
  quickpalette::qp_art[[2]],
  quickpalette::qp_art[[3]],
  quickpalette::qp_art[[4]],
  quickpalette::qp_art[[5]],
  labels = names(quickpalette::qp_art),
  main = "quickpalette"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("EmilHvitfeldt/quickpalette")
```

```{r rcartocolor, fig.height=35}
name <- rcartocolor::cartocolors$Name
pals::pal.bands(
  rcartocolor::carto_pal(name = name[1]),
  rcartocolor::carto_pal(name = name[2]),
  rcartocolor::carto_pal(name = name[3]),
  rcartocolor::carto_pal(name = name[4]),
  rcartocolor::carto_pal(name = name[5]),
  rcartocolor::carto_pal(name = name[6]),
  rcartocolor::carto_pal(name = name[7]),
  rcartocolor::carto_pal(name = name[8]),
  rcartocolor::carto_pal(name = name[9]),
  rcartocolor::carto_pal(name = name[10]),
  rcartocolor::carto_pal(name = name[11]),
  rcartocolor::carto_pal(name = name[12]),
  rcartocolor::carto_pal(name = name[13]),
  rcartocolor::carto_pal(name = name[14]),
  rcartocolor::carto_pal(name = name[15]),
  rcartocolor::carto_pal(name = name[16]),
  rcartocolor::carto_pal(name = name[17]),
  rcartocolor::carto_pal(name = name[18]),
  rcartocolor::carto_pal(name = name[19]),
  rcartocolor::carto_pal(name = name[20]),
  rcartocolor::carto_pal(name = name[21]),
  rcartocolor::carto_pal(name = name[22]),
  rcartocolor::carto_pal(name = name[23]),
  rcartocolor::carto_pal(name = name[24]),
  rcartocolor::carto_pal(name = name[25]),
  rcartocolor::carto_pal(name = name[26]),
  rcartocolor::carto_pal(name = name[27]),
  rcartocolor::carto_pal(name = name[28]),
  rcartocolor::carto_pal(name = name[29]),
  rcartocolor::carto_pal(name = name[30]),
  rcartocolor::carto_pal(name = name[31]),
  rcartocolor::carto_pal(name = name[32]),
  rcartocolor::carto_pal(name = name[33]),
  rcartocolor::carto_pal(name = name[34]),
  labels = name,
  main = "rcartocolor"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewer, fig.height=36}
name <- rownames(RColorBrewer::brewer.pal.info)
ncolor <- RColorBrewer::brewer.pal.info$maxcolors
pals::pal.bands(
  RColorBrewer::brewer.pal(ncolor[1], name[1]),
  RColorBrewer::brewer.pal(ncolor[2], name[2]),
  RColorBrewer::brewer.pal(ncolor[3], name[3]),
  RColorBrewer::brewer.pal(ncolor[4], name[4]),
  RColorBrewer::brewer.pal(ncolor[5], name[5]),
  RColorBrewer::brewer.pal(ncolor[6], name[6]),
  RColorBrewer::brewer.pal(ncolor[7], name[7]),
  RColorBrewer::brewer.pal(ncolor[8], name[8]),
  RColorBrewer::brewer.pal(ncolor[9], name[9]),
  RColorBrewer::brewer.pal(ncolor[10], name[10]),
  RColorBrewer::brewer.pal(ncolor[11], name[11]),
  RColorBrewer::brewer.pal(ncolor[12], name[12]),
  RColorBrewer::brewer.pal(ncolor[13], name[13]),
  RColorBrewer::brewer.pal(ncolor[14], name[14]),
  RColorBrewer::brewer.pal(ncolor[15], name[15]),
  RColorBrewer::brewer.pal(ncolor[16], name[16]),
  RColorBrewer::brewer.pal(ncolor[17], name[17]),
  RColorBrewer::brewer.pal(ncolor[18], name[18]),
  RColorBrewer::brewer.pal(ncolor[19], name[19]),
  RColorBrewer::brewer.pal(ncolor[20], name[20]),
  RColorBrewer::brewer.pal(ncolor[21], name[21]),
  RColorBrewer::brewer.pal(ncolor[22], name[22]),
  RColorBrewer::brewer.pal(ncolor[23], name[23]),
  RColorBrewer::brewer.pal(ncolor[24], name[24]),
  RColorBrewer::brewer.pal(ncolor[25], name[25]),
  RColorBrewer::brewer.pal(ncolor[26], name[26]),
  RColorBrewer::brewer.pal(ncolor[27], name[27]),
  RColorBrewer::brewer.pal(ncolor[28], name[28]),
  RColorBrewer::brewer.pal(ncolor[29], name[29]),
  RColorBrewer::brewer.pal(ncolor[30], name[30]),
  RColorBrewer::brewer.pal(ncolor[31], name[31]),
  RColorBrewer::brewer.pal(ncolor[32], name[32]),
  RColorBrewer::brewer.pal(ncolor[33], name[33]),
  RColorBrewer::brewer.pal(ncolor[34], name[34]),
  RColorBrewer::brewer.pal(ncolor[35], name[35]),
  labels = name,
  main = "RColorBrewer"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonder, fig.height=42}
name <- rownames(Redmonder::redmonder.pal.info)
ncolor <- Redmonder::redmonder.pal.info$maxcolors
pals::pal.bands(
  Redmonder::redmonder.pal(ncolor[1], name[1]),
  Redmonder::redmonder.pal(ncolor[2], name[2]),
  Redmonder::redmonder.pal(ncolor[3], name[3]),
  Redmonder::redmonder.pal(ncolor[4], name[4]),
  Redmonder::redmonder.pal(ncolor[5], name[5]),
  Redmonder::redmonder.pal(ncolor[6], name[6]),
  Redmonder::redmonder.pal(ncolor[7], name[7]),
  Redmonder::redmonder.pal(ncolor[8], name[8]),
  Redmonder::redmonder.pal(ncolor[9], name[9]),
  Redmonder::redmonder.pal(ncolor[10], name[10]),
  Redmonder::redmonder.pal(ncolor[11], name[11]),
  Redmonder::redmonder.pal(ncolor[12], name[12]),
  Redmonder::redmonder.pal(ncolor[13], name[13]),
  Redmonder::redmonder.pal(ncolor[14], name[14]),
  Redmonder::redmonder.pal(ncolor[15], name[15]),
  Redmonder::redmonder.pal(ncolor[16], name[16]),
  Redmonder::redmonder.pal(ncolor[17], name[17]),
  Redmonder::redmonder.pal(ncolor[18], name[18]),
  Redmonder::redmonder.pal(ncolor[19], name[19]),
  Redmonder::redmonder.pal(ncolor[20], name[20]),
  Redmonder::redmonder.pal(ncolor[21], name[21]),
  Redmonder::redmonder.pal(ncolor[22], name[22]),
  Redmonder::redmonder.pal(ncolor[23], name[23]),
  Redmonder::redmonder.pal(ncolor[24], name[24]),
  Redmonder::redmonder.pal(ncolor[25], name[25]),
  Redmonder::redmonder.pal(ncolor[26], name[26]),
  Redmonder::redmonder.pal(ncolor[27], name[27]),
  Redmonder::redmonder.pal(ncolor[28], name[28]),
  Redmonder::redmonder.pal(ncolor[29], name[29]),
  Redmonder::redmonder.pal(ncolor[30], name[30]),
  Redmonder::redmonder.pal(ncolor[31], name[31]),
  Redmonder::redmonder.pal(ncolor[32], name[32]),
  Redmonder::redmonder.pal(ncolor[33], name[33]),
  Redmonder::redmonder.pal(ncolor[34], name[34]),
  Redmonder::redmonder.pal(ncolor[35], name[35]),
  Redmonder::redmonder.pal(ncolor[36], name[36]),
  Redmonder::redmonder.pal(ncolor[37], name[37]),
  Redmonder::redmonder.pal(ncolor[38], name[38]),
  Redmonder::redmonder.pal(ncolor[39], name[39]),
  Redmonder::redmonder.pal(ncolor[40], name[40]),
  Redmonder::redmonder.pal(ncolor[41], name[41]),
  labels = name,
  main = "Redmonder"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r RSkittleBrewer, fig.height=6}
pals::pal.bands(RSkittleBrewer::RSkittleBrewer("original"),
                RSkittleBrewer::RSkittleBrewer("tropical"),
                RSkittleBrewer::RSkittleBrewer("wildberry"),
                RSkittleBrewer::RSkittleBrewer("M&M"),
                unname(RSkittleBrewer::RSkittleBrewer("smarties")),
                labels = c("original", "tropical", "wildberry", "M&M", "smarties"),
                main = "RSkittleBrewer")
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("alyssafrazee/RSkittleBrewer")
```

```{r viridis, fig.height=6}
pals::pal.bands(
  viridis::cividis,
  viridis::inferno, 
  viridis::magma, 
  viridis::plasma,
  viridis::viridis, 
  labels = c("civiris", "inferno", "magma", "plasma", "viridis"), 
  main = "Viridis"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("sjmgarnier/viridis")
# CRAN version
install.packages("viridis")
```

```{r wesanderson, fig.height=16}
pals::pal.bands(
  wesanderson::wes_palettes[[1]],
  wesanderson::wes_palettes[[2]],
  wesanderson::wes_palettes[[3]],
  wesanderson::wes_palettes[[4]],
  wesanderson::wes_palettes[[5]],
  wesanderson::wes_palettes[[6]],
  wesanderson::wes_palettes[[7]],
  wesanderson::wes_palettes[[8]],
  wesanderson::wes_palettes[[9]],
  wesanderson::wes_palettes[[10]],
  wesanderson::wes_palettes[[11]],
  wesanderson::wes_palettes[[12]],
  wesanderson::wes_palettes[[13]],
  wesanderson::wes_palettes[[14]],
  wesanderson::wes_palettes[[15]],
  labels = names(wesanderson::wes_palettes),
  main = "wesanderson"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("karthik/wesanderson")
# CRAN version
install.packages("wesanderson")
```

```{r yarrr, fig.height=22}
pals::pal.bands(
  unname(yarrr::piratepal("basel")),
  unname(yarrr::piratepal("pony")),
  unname(yarrr::piratepal("xmen")),
  unname(yarrr::piratepal("decision")),
  unname(yarrr::piratepal("southpark")),
  unname(yarrr::piratepal("google")),
  unname(yarrr::piratepal("eternal")),
  unname(yarrr::piratepal("evildead")),
  unname(yarrr::piratepal("usualsuspects")),
  unname(yarrr::piratepal("ohbrother")),
  unname(yarrr::piratepal("appletv")),
  unname(yarrr::piratepal("brave")),
  unname(yarrr::piratepal("bugs")),
  unname(yarrr::piratepal("cars")),
  unname(yarrr::piratepal("nemo")),
  unname(yarrr::piratepal("rat")),
  unname(yarrr::piratepal("up")),
  unname(yarrr::piratepal("espresso")),
  unname(yarrr::piratepal("ipod")),
  unname(yarrr::piratepal("info")),
  unname(yarrr::piratepal("info2")),
  labels = yarrr::piratepal("names"),
  main = "yarrr"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ndphillips/yarrr")
# CRAN version
install.packages("yarrr")
```
