---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, cache = TRUE, fig.width = 7,
               fig.path = "man/figures/type-sorted-")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

## Palettes sorted by type (Sequential/Diverging/Qualitative)

Table of Contents
=================
  * [Main page](README.md#comprehensive-list-of-color-palettes-in-r)
  * [Blogposts and other resources](README.md#blogposts-and-other-resources)
  * [Generative packages](README.md#generative-packages)
  * [Honorable mentions](README.md#honorable-mentions)
  * [Palettes sorted by Package (alphabetically)](README.md#palettes-sorted-by-package-alphabetically)
    * [Sequential color palettes](#sequential-color-palettes)
    * [Diverging color palettes](#diverging-color-palettes)
    * [Qualitative color palettes](#qualitative-color-palettes)

### Sequential color palettes

```{r awtoolsseq, fig.height=3}
pals::pal.bands(awtools::a_palette,
                awtools::a_spalette,
                labels = c("a_palette", "a_spalette"),
                main = "awtools")
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("awhstin/awtools")
```

```{r cividisseq, fig.height=2.5}
pals::pal.bands(viridisLite::cividis,
                labels = "cividis",
                main = "cividis")
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("marcosci/cividis")
```

```{r ggsciseq, fig.height=20}
pals::pal.bands(
  ggsci::pal_material("red")(10),
  ggsci::pal_material("pink")(10),
  ggsci::pal_material("purple")(10),
  ggsci::pal_material("deep-purple")(10),
  ggsci::pal_material("indigo")(10),
  ggsci::pal_material("blue")(10),
  ggsci::pal_material("light-blue")(10),
  ggsci::pal_material("cyan")(10),
  ggsci::pal_material("teal")(10),
  ggsci::pal_material("green")(10),
  ggsci::pal_material("light-green")(10),
  ggsci::pal_material("lime")(10),
  ggsci::pal_material("yellow")(10),
  ggsci::pal_material("amber")(10),
  ggsci::pal_material("orange")(10),
  ggsci::pal_material("deep-orange")(10),
  ggsci::pal_material("brown")(10),
  ggsci::pal_material("grey")(10),
  ggsci::pal_material("blue-grey")(10),
  labels = c("material-red", "material-pink", "material-purple", 
             "material-deep-purple", "material-indigo", "material-blue",
             "material-light-blue", "material-cyan", "material-teal", 
             "material-green", "material-light-green", "material-lime",
             "material-yellow", "material-amber", "material-orange",
             "material-deep-orange", "material-brown", "material-grey",
             "material-blue-grey"),
  main = "ggsci"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r grDevicesseq, fig.height=3}
pals::pal.bands(
  grDevices::blues9,
  heat.colors(100),
  labels = c("blues9", "heat.colors"),
  main = "grDevices"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("grDevices")
```

```{r nordseq, fig.height=4}
pals::pal.bands(
  nord::nord_palettes[[1]],
  nord::nord_palettes[[2]],
  nord::nord_palettes[[10]],
  labels = names(nord::nord_palettes)[c(1, 2, 10)],
  main = "nord"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r oompaBaseseq, fig.height=5}
pals::pal.bands(
  oompaBase::redscale(100),
  oompaBase::greenscale(100),
  oompaBase::bluescale(100),
  oompaBase::greyscale(100),
  labels = c("redscale", "greenscale", "bluescale", "greyscale"),
  main = "oompaBase"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("oompaBase")
```

```{r palscontinuousseq, fig.height=4}
pals::pal.bands(
  pals::cubehelix,
  pals::gnuplot,
  pals::parula,
  labels = c("cubehelix", "gnuplot", "parula"),
  main = "pals (Continuous)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsniccoliseq, fig.height=6}
pals::pal.bands(
  pals::cubicyf,
  pals::cubicl,
  pals::isol,
  pals::linearl,
  pals::linearlhot,
  labels = c("cubicyf", "cubicl", "isol", "linearl", "linearlhot"),
  main = "pals (Niccoli)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsoceanseq, fig.height=16}
pals::pal.bands(
  pals::ocean.thermal, 
  pals::ocean.haline, 
  pals::ocean.solar, 
  pals::ocean.ice, 
  pals::ocean.gray,
  pals::ocean.oxy, 
  pals::ocean.deep, 
  pals::ocean.dense, 
  pals::ocean.algae, 
  pals::ocean.matter,
  pals::ocean.turbid, 
  pals::ocean.speed, 
  pals::ocean.amp, 
  pals::ocean.tempo, 
  pals::ocean.phase,
  labels = c("thermal", "haline", "solar", "ice", "gray", "oxy", "deep", "dense",
             "algae", "matter", "turbid", "speed", "amp", "tempo", "phase"),
  main = "pals (Ocean)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovosiseq, message=FALSE, fig.height=25}
library(pals)
pal.bands(
  kovesi.cyclic_grey_15_85_c0, kovesi.cyclic_grey_15_85_c0_s25,
  kovesi.cyclic_mrybm_35_75_c68, kovesi.cyclic_mrybm_35_75_c68_s25,
  kovesi.cyclic_mygbm_30_95_c78, kovesi.cyclic_mygbm_30_95_c78_s25,
  kovesi.cyclic_wrwbw_40_90_c42, kovesi.cyclic_wrwbw_40_90_c42_s25,
  kovesi.diverging_isoluminant_cjm_75_c23, kovesi.diverging_isoluminant_cjm_75_c24,
  kovesi.diverging_isoluminant_cjo_70_c25, kovesi.diverging_linear_bjr_30_55_c53,
  kovesi.diverging_linear_bjy_30_90_c45, kovesi.diverging_rainbow_bgymr_45_85_c67,
  kovesi.diverging_gkr_60_10_c40,
  kovesi.diverging_gwr_55_95_c38, kovesi.diverging_gwv_55_95_c39,
  kovesi.isoluminant_cgo_70_c39, kovesi.isoluminant_cgo_80_c38,
  kovesi.isoluminant_cm_70_c39, kovesi.rainbow_bgyr_35_85_c72, kovesi.rainbow_bgyr_35_85_c73,
  kovesi.rainbow_bgyrm_35_85_c69, kovesi.rainbow_bgyrm_35_85_c71,
  main = "pals (Kovesi)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovisilinearseq, fig.height=22}
library(pals)
pal.bands(
  kovesi.linear_bgy_10_95_c74, kovesi.linear_bgyw_15_100_c67, 
  kovesi.linear_bgyw_15_100_c68, kovesi.linear_blue_5_95_c73, 
  kovesi.linear_blue_95_50_c20, kovesi.linear_bmw_5_95_c86,
  kovesi.linear_bmw_5_95_c89, kovesi.linear_bmy_10_95_c71,
  kovesi.linear_bmy_10_95_c78, kovesi.linear_gow_60_85_c27,
  kovesi.linear_gow_65_90_c35, kovesi.linear_green_5_95_c69, 
  kovesi.linear_grey_0_100_c0, kovesi.linear_grey_10_95_c0,
  kovesi.linear_kry_5_95_c72, kovesi.linear_kry_5_98_c75,
  kovesi.linear_kryw_5_100_c64, kovesi.linear_kryw_5_100_c67,
  kovesi.linear_ternary_blue_0_44_c57, kovesi.linear_ternary_green_0_46_c42,
  kovesi.linear_ternary_red_0_50_c52,
  main = "pals (Kovesi linear)"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r rcartocolorseq, fig.height=22}
name <- rcartocolor::cartocolors$Name
pals::pal.bands(
  rcartocolor::carto_pal(name = name[1]),
  rcartocolor::carto_pal(name = name[2]),
  rcartocolor::carto_pal(name = name[16]),
  rcartocolor::carto_pal(name = name[17]),
  rcartocolor::carto_pal(name = name[18]),
  rcartocolor::carto_pal(name = name[19]),
  rcartocolor::carto_pal(name = name[20]),
  rcartocolor::carto_pal(name = name[21]),
  rcartocolor::carto_pal(name = name[22]),
  rcartocolor::carto_pal(name = name[23]),
  rcartocolor::carto_pal(name = name[24]),
  rcartocolor::carto_pal(name = name[25]),
  rcartocolor::carto_pal(name = name[26]),
  rcartocolor::carto_pal(name = name[27]),
  rcartocolor::carto_pal(name = name[28]),
  rcartocolor::carto_pal(name = name[29]),
  rcartocolor::carto_pal(name = name[30]),
  rcartocolor::carto_pal(name = name[31]),
  rcartocolor::carto_pal(name = name[32]),
  rcartocolor::carto_pal(name = name[33]),
  rcartocolor::carto_pal(name = name[34]),
  labels = name[c(1,2, 16:34)],
  main = "rcartocolor"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerseq, fig.height=19}
name <- rownames(RColorBrewer::brewer.pal.info)
ncolor <- RColorBrewer::brewer.pal.info$maxcolors
pals::pal.bands(
  RColorBrewer::brewer.pal(ncolor[18], name[18]),
  RColorBrewer::brewer.pal(ncolor[19], name[19]),
  RColorBrewer::brewer.pal(ncolor[20], name[20]),
  RColorBrewer::brewer.pal(ncolor[21], name[21]),
  RColorBrewer::brewer.pal(ncolor[22], name[22]),
  RColorBrewer::brewer.pal(ncolor[23], name[23]),
  RColorBrewer::brewer.pal(ncolor[24], name[24]),
  RColorBrewer::brewer.pal(ncolor[25], name[25]),
  RColorBrewer::brewer.pal(ncolor[26], name[26]),
  RColorBrewer::brewer.pal(ncolor[27], name[27]),
  RColorBrewer::brewer.pal(ncolor[28], name[28]),
  RColorBrewer::brewer.pal(ncolor[29], name[29]),
  RColorBrewer::brewer.pal(ncolor[30], name[30]),
  RColorBrewer::brewer.pal(ncolor[31], name[31]),
  RColorBrewer::brewer.pal(ncolor[32], name[32]),
  RColorBrewer::brewer.pal(ncolor[33], name[33]),
  RColorBrewer::brewer.pal(ncolor[34], name[34]),
  RColorBrewer::brewer.pal(ncolor[35], name[35]),
  labels = name[18:35],
  main = "RColorBrewer"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderseq, fig.height=11}
name <- rownames(Redmonder::redmonder.pal.info)
ncolor <- Redmonder::redmonder.pal.info$maxcolors
pals::pal.bands(
  Redmonder::redmonder.pal(ncolor[32], name[32]),
  Redmonder::redmonder.pal(ncolor[33], name[33]),
  Redmonder::redmonder.pal(ncolor[34], name[34]),
  Redmonder::redmonder.pal(ncolor[35], name[35]),
  Redmonder::redmonder.pal(ncolor[36], name[36]),
  Redmonder::redmonder.pal(ncolor[37], name[37]),
  Redmonder::redmonder.pal(ncolor[38], name[38]),
  Redmonder::redmonder.pal(ncolor[39], name[39]),
  Redmonder::redmonder.pal(ncolor[40], name[40]),
  Redmonder::redmonder.pal(ncolor[41], name[41]),
  labels = name[32:41],
  main = "Redmonder"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r viridisseq, fig.height=5}
pals::pal.bands(
  viridis::inferno, 
  viridis::magma, 
  viridis::plasma,
  viridis::viridis, 
  labels = c("inferno", "magma", "plasma", "viridis"), 
  main = "Viridis"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("sjmgarnier/viridis")
# CRAN version
install.packages("viridis")
```

### Diverging color palettes

```{r ggscidiv, fig.height=2.5}
pals::pal.bands(
  ggsci::pal_gsea("default")(12),
  labels = c("gsea"),
  main = "ggsci"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r grDevicesdiv, fig.height=2.5}
pals::pal.bands(
  cm.colors(100),
  labels = c("cm.colors"),
  main = "grDevices"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("grDevices")
```

```{r norddiv, fig.height=3}
pals::pal.bands(
  nord::nord_palettes[[6]],
  nord::nord_palettes[[7]],
  labels = names(nord::nord_palettes)[6:7],
  main = "nord"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r oompaBasediv, fig.height=4}
pals::pal.bands(
  oompaBase::blueyellow(100),
  oompaBase::cyanyellow(100),
  oompaBase::redgreen(100),
  labels = c("blueyellow", "cyanyellow", "redgreen"),
  main = "oompaBase"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("oompaBase")
```

```{r palscontinuousdiv, fig.height=3}
pals::pal.bands(
  pals::coolwarm,
  pals::warmcool,
  labels = c("coolwarm", "warmcool"),
  main = "pals (Continuous)", n = 100
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsoceandiv, fig.height=4}
pals::pal.bands(
  pals::ocean.balance, 
  pals::ocean.delta, 
  pals::ocean.curl, 
  labels = c("balance", "delta", "curl"),
  main = "pals (Ocean)", n = 100
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovosidiv, message=FALSE, fig.height=14}
library(pals)
pal.bands(
  kovesi.diverging_isoluminant_cjm_75_c23, kovesi.diverging_isoluminant_cjm_75_c24,
  kovesi.diverging_isoluminant_cjo_70_c25, kovesi.diverging_linear_bjr_30_55_c53,
  kovesi.diverging_linear_bjy_30_90_c45,
  kovesi.diverging_bkr_55_10_c35, kovesi.diverging_bky_60_10_c30,
  kovesi.diverging_bwr_40_95_c42, kovesi.diverging_bwr_55_98_c37,
  kovesi.diverging_cwm_80_100_c22, kovesi.diverging_gkr_60_10_c40,
  kovesi.diverging_gwr_55_95_c38, kovesi.diverging_gwv_55_95_c39,
  main = "pals (Kovesi)", n = 100
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r rcartocolordiv, fig.height=8}
name <- rcartocolor::cartocolors$Name
pals::pal.bands(
  rcartocolor::carto_pal(name = name[3]),
  rcartocolor::carto_pal(name = name[4]),
  rcartocolor::carto_pal(name = name[5]),
  rcartocolor::carto_pal(name = name[6]),
  rcartocolor::carto_pal(name = name[7]),
  rcartocolor::carto_pal(name = name[8]),
  rcartocolor::carto_pal(name = name[9]),
  labels = name[3:9],
  main = "rcartocolor"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerdiv, fig.height=10}
name <- rownames(RColorBrewer::brewer.pal.info)
ncolor <- RColorBrewer::brewer.pal.info$maxcolors
pals::pal.bands(
  RColorBrewer::brewer.pal(ncolor[1], name[1]),
  RColorBrewer::brewer.pal(ncolor[2], name[2]),
  RColorBrewer::brewer.pal(ncolor[3], name[3]),
  RColorBrewer::brewer.pal(ncolor[4], name[4]),
  RColorBrewer::brewer.pal(ncolor[5], name[5]),
  RColorBrewer::brewer.pal(ncolor[6], name[6]),
  RColorBrewer::brewer.pal(ncolor[7], name[7]),
  RColorBrewer::brewer.pal(ncolor[8], name[8]),
  RColorBrewer::brewer.pal(ncolor[9], name[9]),
  labels = name[1:9],
  main = "RColorBrewer"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderdiv, fig.height=8}
name <- rownames(Redmonder::redmonder.pal.info)
ncolor <- Redmonder::redmonder.pal.info$maxcolors
pals::pal.bands(
  Redmonder::redmonder.pal(ncolor[1], name[1]),
  Redmonder::redmonder.pal(ncolor[2], name[2]),
  Redmonder::redmonder.pal(ncolor[3], name[3]),
  Redmonder::redmonder.pal(ncolor[4], name[4]),
  Redmonder::redmonder.pal(ncolor[5], name[5]),
  Redmonder::redmonder.pal(ncolor[6], name[6]),
  Redmonder::redmonder.pal(ncolor[7], name[7]),
  labels = name[1:7],
  main = "Redmonder"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

### Qualitative color palettes

```{r awtoolsqua, fig.height=4}
pals::pal.bands(
  awtools::mpalette,
  awtools::ppalette,
  awtools::spalette,
  labels = c("mpalette", "ppalette", 
             "spalette"),
  main = "awtools"
  )
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("awhstin/awtools")
```

```{r dutchmastersqua, fig.height=7}
pals::pal.bands(
  unname(dutchmasters::dutchmasters[[1]]),
  unname(dutchmasters::dutchmasters[[2]]),
  unname(dutchmasters::dutchmasters[[3]]),
  unname(dutchmasters::dutchmasters[[4]]),
  unname(dutchmasters::dutchmasters[[5]]),
  unname(dutchmasters::dutchmasters[[6]]),
  labels = names(dutchmasters::dutchmasters),
  main = "dutchmasters"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("EdwinTh/dutchmasters")
```

```{r ggsciqua, fig.height=23}
pals::pal.bands(
  ggsci::pal_npg("nrc")(10),
  ggsci::pal_aaas("default")(10),
  ggsci::pal_nejm("default")(8),
  ggsci::pal_lancet("lanonc")(9),
  ggsci::pal_jama("default")(7),
  ggsci::pal_jco("default")(10),
  ggsci::pal_ucscgb("default")(26),
  ggsci::pal_d3("category10")(10),
  ggsci::pal_d3("category20")(20),
  ggsci::pal_d3("category20b")(20),
  ggsci::pal_d3("category20c")(20),
  ggsci::pal_locuszoom("default")(7),
  ggsci::pal_igv("default")(51),
  ggsci::pal_igv("alternating")(2),
  ggsci::pal_uchicago("default")(9),
  ggsci::pal_uchicago("light")(9),
  ggsci::pal_uchicago("dark")(9),
  ggsci::pal_startrek("uniform")(7),
  ggsci::pal_tron("legacy")(7),
  ggsci::pal_futurama("planetexpress")(12),
  ggsci::pal_rickandmorty("schwifty")(12),
  ggsci::pal_simpsons("springfield")(16),
  labels = c("npg", "aaas", "nejm", "lancet", "jama", "jco", "ucscgb", 
             "d3-category10", "d3-category20", "d3-category20b", 
             "d3-category20c", "locuszoom", "igv-default", "igv-alternative",
             "uchicago-default", "uchicago-light", "uchicago-dark", "startrek",
             "tron", "futurama", "rickandmorty", "simpsoms"),
  main = "ggsci"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r ghibliqua, fig.height=28}
pals::pal.bands(
  ghibli::ghibli_palettes[[1]],
  ghibli::ghibli_palettes[[2]],
  ghibli::ghibli_palettes[[3]],
  ghibli::ghibli_palettes[[4]],
  ghibli::ghibli_palettes[[5]],
  ghibli::ghibli_palettes[[6]],
  ghibli::ghibli_palettes[[7]],
  ghibli::ghibli_palettes[[8]],
  ghibli::ghibli_palettes[[9]],
  ghibli::ghibli_palettes[[10]],
  ghibli::ghibli_palettes[[11]],
  ghibli::ghibli_palettes[[12]],
  ghibli::ghibli_palettes[[13]],
  ghibli::ghibli_palettes[[14]],
  ghibli::ghibli_palettes[[15]],
  ghibli::ghibli_palettes[[16]],
  ghibli::ghibli_palettes[[17]],
  ghibli::ghibli_palettes[[18]],
  ghibli::ghibli_palettes[[19]],
  ghibli::ghibli_palettes[[20]],
  ghibli::ghibli_palettes[[21]],
  ghibli::ghibli_palettes[[22]],
  ghibli::ghibli_palettes[[23]],
  ghibli::ghibli_palettes[[24]],
  ghibli::ghibli_palettes[[25]],
  ghibli::ghibli_palettes[[26]],
  ghibli::ghibli_palettes[[27]],
  labels = names(ghibli::ghibli_palettes),
  main = "ghibli"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ewenme/ghibli")
# CRAN version
install.packages("ghibli")
```

```{r nordqua, fig.height=12}
pals::pal.bands(
  nord::nord_palettes[[3]],
  nord::nord_palettes[[4]],
  nord::nord_palettes[[5]],
  nord::nord_palettes[[8]],
  nord::nord_palettes[[9]],
  nord::nord_palettes[[11]],
  nord::nord_palettes[[12]],
  nord::nord_palettes[[13]],
  nord::nord_palettes[[14]],
  nord::nord_palettes[[15]],
  nord::nord_palettes[[16]],
  labels = names(nord::nord_palettes)[c(3:5, 8:9, 11:16)],
  main = "nord"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r ochRequa, fig.height=17}
pals::pal.bands(
  unname(ochRe::ochre_palettes[[1]]),
  unname(ochRe::ochre_palettes[[2]]),
  unname(ochRe::ochre_palettes[[3]]),
  unname(ochRe::ochre_palettes[[4]]),
  unname(ochRe::ochre_palettes[[5]]),
  unname(ochRe::ochre_palettes[[6]]),
  unname(ochRe::ochre_palettes[[7]]),
  unname(ochRe::ochre_palettes[[8]]),
  unname(ochRe::ochre_palettes[[9]]),
  unname(ochRe::ochre_palettes[[10]]),
  unname(ochRe::ochre_palettes[[11]]),
  unname(ochRe::ochre_palettes[[12]]),
  unname(ochRe::ochre_palettes[[13]]),
  unname(ochRe::ochre_palettes[[14]]),
  unname(ochRe::ochre_palettes[[15]]),
  unname(ochRe::ochre_palettes[[16]]),
  labels = names(ochRe::ochre_palettes),
  main = "ochRe"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ropenscilabs/ochRe")
# CRAN version
install.packages("ochRe")
```

```{r palettetownqua, fig.height=11}
ids <- c(6, 17, 114, 137, 156, 191, 193, 283, 311, 318)
names <- c("charizard", "pidgeotto", "tangela", "porygon", "quilava", 
           "sunkern", "yanma", "surskit", "plusle", "carvanha")

pals::pal.bands(
  palettetown::ichooseyou(ids[1]),
  palettetown::ichooseyou(ids[2]),
  palettetown::ichooseyou(ids[3]),
  palettetown::ichooseyou(ids[4]),
  palettetown::ichooseyou(ids[5]),
  palettetown::ichooseyou(ids[6]),
  palettetown::ichooseyou(ids[7]),
  palettetown::ichooseyou(ids[8]),
  palettetown::ichooseyou(ids[9]),
  palettetown::ichooseyou(ids[10]),
  labels = stringr::str_c(ids, " - ", names),
  main = "palettetown"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("timcdlucas/palettetown")
# CRAN version
install.packages("palettetown")
```

```{r palsdiscretequa, fig.height=9}
pals::pal.bands(
  pals::alphabet(), 
  pals::alphabet2(), 
  pals::glasbey(), 
  pals::kelly(),
  pals::polychrome(), 
  pals::stepped(), 
  pals::tol(), 
  pals::watlington(), 
  labels = c('alphabet','alphabet2', 'glasbey','kelly','polychrome', 'stepped',
             'tol', 'watlington'), 
  main = "pals (Discrete)",
  show.names = FALSE
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r Polychromequa, fig.height=8}
pals::pal.bands(
  Polychrome::alphabet.colors(),
  Polychrome::dark.colors(),
  Polychrome::glasbey.colors(),
  Polychrome::green.armytage.colors(),
  Polychrome::kelly.colors(),
  Polychrome::light.colors(),
  Polychrome::palette36.colors(),
  show.names = FALSE,
  labels = c("alphabet", "dark", "glasbey", "green armytage", "kelly", "light",
             "palette36"),
  main = "Polychrome"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Polychrome")
```

```{r rcartocolorqua, fig.height=7}
name <- rcartocolor::cartocolors$Name
pals::pal.bands(
  rcartocolor::carto_pal(name = name[10]),
  rcartocolor::carto_pal(name = name[11]),
  rcartocolor::carto_pal(name = name[12]),
  rcartocolor::carto_pal(name = name[13]),
  rcartocolor::carto_pal(name = name[14]),
  rcartocolor::carto_pal(name = name[15]),
  labels = name[10:15],
  main = "rcartocolor"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerqua, fig.height=9}
name <- rownames(RColorBrewer::brewer.pal.info)
ncolor <- RColorBrewer::brewer.pal.info$maxcolors
pals::pal.bands(
  RColorBrewer::brewer.pal(ncolor[10], name[10]),
  RColorBrewer::brewer.pal(ncolor[11], name[11]),
  RColorBrewer::brewer.pal(ncolor[12], name[12]),
  RColorBrewer::brewer.pal(ncolor[13], name[13]),
  RColorBrewer::brewer.pal(ncolor[14], name[14]),
  RColorBrewer::brewer.pal(ncolor[15], name[15]),
  RColorBrewer::brewer.pal(ncolor[16], name[16]),
  RColorBrewer::brewer.pal(ncolor[17], name[17]),
  labels = name[10:17],
  main = "RColorBrewer"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderqua, fig.height=25}
name <- rownames(Redmonder::redmonder.pal.info)
ncolor <- Redmonder::redmonder.pal.info$maxcolors
pals::pal.bands(
  Redmonder::redmonder.pal(ncolor[8], name[8]),
  Redmonder::redmonder.pal(ncolor[9], name[9]),
  Redmonder::redmonder.pal(ncolor[10], name[10]),
  Redmonder::redmonder.pal(ncolor[11], name[11]),
  Redmonder::redmonder.pal(ncolor[12], name[12]),
  Redmonder::redmonder.pal(ncolor[13], name[13]),
  Redmonder::redmonder.pal(ncolor[14], name[14]),
  Redmonder::redmonder.pal(ncolor[15], name[15]),
  Redmonder::redmonder.pal(ncolor[16], name[16]),
  Redmonder::redmonder.pal(ncolor[17], name[17]),
  Redmonder::redmonder.pal(ncolor[18], name[18]),
  Redmonder::redmonder.pal(ncolor[19], name[19]),
  Redmonder::redmonder.pal(ncolor[20], name[20]),
  Redmonder::redmonder.pal(ncolor[21], name[21]),
  Redmonder::redmonder.pal(ncolor[22], name[22]),
  Redmonder::redmonder.pal(ncolor[23], name[23]),
  Redmonder::redmonder.pal(ncolor[24], name[24]),
  Redmonder::redmonder.pal(ncolor[25], name[25]),
  Redmonder::redmonder.pal(ncolor[26], name[26]),
  Redmonder::redmonder.pal(ncolor[27], name[27]),
  Redmonder::redmonder.pal(ncolor[28], name[28]),
  Redmonder::redmonder.pal(ncolor[29], name[29]),
  Redmonder::redmonder.pal(ncolor[30], name[30]),
  Redmonder::redmonder.pal(ncolor[31], name[31]),
  labels = name[8:31],
  main = "Redmonder"
)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r RSkittleBrewerqua, fig.height=6}
pals::pal.bands(RSkittleBrewer::RSkittleBrewer("original"),
                RSkittleBrewer::RSkittleBrewer("tropical"),
                RSkittleBrewer::RSkittleBrewer("wildberry"),
                RSkittleBrewer::RSkittleBrewer("M&M"),
                unname(RSkittleBrewer::RSkittleBrewer("smarties")),
                labels = c("original", "tropical", "wildberry", "M&M", "smarties"),
                main = "RSkittleBrewer")
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("alyssafrazee/RSkittleBrewer")
```

```{r wesandersonqua, fig.height=16}
pals::pal.bands(
  wesanderson::wes_palettes[[1]],
  wesanderson::wes_palettes[[2]],
  wesanderson::wes_palettes[[3]],
  wesanderson::wes_palettes[[4]],
  wesanderson::wes_palettes[[5]],
  wesanderson::wes_palettes[[6]],
  wesanderson::wes_palettes[[7]],
  wesanderson::wes_palettes[[8]],
  wesanderson::wes_palettes[[9]],
  wesanderson::wes_palettes[[10]],
  wesanderson::wes_palettes[[11]],
  wesanderson::wes_palettes[[12]],
  wesanderson::wes_palettes[[13]],
  wesanderson::wes_palettes[[14]],
  wesanderson::wes_palettes[[15]],
  labels = names(wesanderson::wes_palettes),
  main = "wesanderson"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("karthik/wesanderson")
# CRAN version
install.packages("wesanderson")
```

```{r yarrrqua, fig.height=22}
pals::pal.bands(
  unname(yarrr::piratepal("basel")),
  unname(yarrr::piratepal("pony")),
  unname(yarrr::piratepal("xmen")),
  unname(yarrr::piratepal("decision")),
  unname(yarrr::piratepal("southpark")),
  unname(yarrr::piratepal("google")),
  unname(yarrr::piratepal("eternal")),
  unname(yarrr::piratepal("evildead")),
  unname(yarrr::piratepal("usualsuspects")),
  unname(yarrr::piratepal("ohbrother")),
  unname(yarrr::piratepal("appletv")),
  unname(yarrr::piratepal("brave")),
  unname(yarrr::piratepal("bugs")),
  unname(yarrr::piratepal("cars")),
  unname(yarrr::piratepal("nemo")),
  unname(yarrr::piratepal("rat")),
  unname(yarrr::piratepal("up")),
  unname(yarrr::piratepal("espresso")),
  unname(yarrr::piratepal("ipod")),
  unname(yarrr::piratepal("info")),
  unname(yarrr::piratepal("info2")),
  labels = yarrr::piratepal("names"),
  main = "yarrr"
)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ndphillips/yarrr")
# CRAN version
install.packages("yarrr")
```