---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, fig.width = 7,
               fig.path = "man/figures/type-sorted-")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5", cache = TRUE)
```

```{r include=FALSE}
library(paletteer)
source("R/list_plotter.R")
```

## Palettes sorted by type (Sequential/Diverging/Qualitative)

Table of Contents
=================
  * [Main page](README.md#comprehensive-list-of-color-palettes-in-r)
  * [Blogposts and other resources](README.md#blogposts-and-other-resources)
  * [Color manipulation packages](README.md#color-manipulation-packages)
  * [Generative packages](README.md#generative-packages)
  * [Perception of color palettes](README.md#perception-of-color-palettes)
    * [Printing in black and white](README.md#printing-in-black-and-white)
    * [Color blindness](README.md#color-blindness)
  * [Honorable mentions](README.md#honorable-mentions)
  * [Palettes sorted by Package (alphabetically)](README.md#palettes-sorted-by-package-alphabetically)
    * [Sequential color palettes](#sequential-color-palettes)
    * [Diverging color palettes](#diverging-color-palettes)
    * [Qualitative color palettes](#qualitative-color-palettes)
    * [Canva palettes](canva.md)
    * [Palettetown palettes](palettetown.md)
  * [News](NEWS.md)

### Sequential color palettes

```{r cartographyseq, fig.height=15}
package_name <- "cartography"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("riatelab/cartography")
# CRAN version
install.packages("cartography")
```

```{r dichromatseq, fig.height=4}
package_name <- "dichromat"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("dichromat")
```


```{r ggsciseq, fig.height=20}
package_name <- "ggsci"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r ggthemestableauseq, fig.height=19}
package_name <- "ggthemes"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jrnold/ggthemes")
# CRAN version
install.packages("ggthemes")
```

```{r grDevicesseq, fig.height=6}
package_name <- "grDevices"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("grDevices")
```

```{r jcolors-discreteseq, fig.height=4}
package_name <- "jcolors"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jaredhuling/jcolors")
# CRAN version
install.packages("jcolors")
```

```{r jcolors-continseq, fig.height=9}
package_name <- "jcolors"
palette_names <- c("default", "pal2", "pal3", "pal4", "pal10", "pal11", "pal12", "rainbow")

pal_data <- list(names = palette_names,
                 color = purrr::map(palette_names, ~ jcolors::jcolors_contin(palette = .x)(256)))

list_plotter(pal_data$color, pal_data$names, "jcolors (continuous)")
```

the `jcolors` continuous palettes are currently not available in the `paletteer` package. 

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jaredhuling/jcolors")
# CRAN version
install.packages("jcolors")
```

```{r nordseq, fig.height=4}
package_name <- "nord"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r oompaBaseseq, fig.height=6}
package_name <- "oompaBase"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("oompaBase")
```

```{r palrseq, fig.height=5}
package_name <- "palr"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("AustralianAntarcticDivision/palr")
# CRAN version
install.packages("palr")
```

```{r palscontinuousseq, fig.height=23}
package_name <- "pals"
pal_data <- all_names(package_name, "sequential")
ids <- !stringr::str_detect(pal_data$names, "kovesi")

list_plotter(pal_data$color[ids], pal_data$names[ids], package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palsniccoliseq, fig.height=38}
package_name <- "pals"
pal_data <- all_names(package_name, "sequential")
ids <- stringr::str_detect(pal_data$names, "kovesi")

list_plotter(pal_data$color[ids], pal_data$names[ids], package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r rcartocolorseq, fig.height=22}
package_name <- "rcartocolor"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerseq, fig.height=19}
package_name <- "RColorBrewer"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderseq, fig.height=11}
package_name <- "Redmonder"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r scicoseq, fig.height=12}
package_name <- "scico"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("thomasp85/scico")
# CRAN version
install.packages("scico")
```

```{r viridisseq, fig.height=6}
package_name <- "viridis"
pal_data <- all_names(package_name, "sequential")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("sjmgarnier/viridis")
# CRAN version
install.packages("viridis")
```

### Diverging color palettes

```{r dichromatdiv, fig.height=14}
package_name <- "dichromat"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("dichromat")
```

```{r ggscidiv, fig.height=2.5}
package_name <- "ggsci"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r ggthemestableaudiv, fig.height=17}
package_name <- "ggthemes"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jrnold/ggthemes")
# CRAN version
install.packages("ggthemes")
```

```{r grDevicesdiv, fig.height=2.5}
package_name <- "grDevices"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("grDevices")
```

```{r norddiv, fig.height=3}
package_name <- "nord"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r oompaBasediv, fig.height=4}
package_name <- "oompaBase"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("oompaBase")
```

```{r palsoceandiv, fig.height=6}
package_name <- "pals"
pal_data <- all_names(package_name, "diverging")
ids <- !stringr::str_detect(pal_data$names, "kovesi")

list_plotter(pal_data$color[ids], pal_data$names[ids], package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r palskovosidiv, message=FALSE, fig.height=14}
package_name <- "pals"
pal_data <- all_names(package_name, "diverging")
ids <- stringr::str_detect(pal_data$names, "kovesi")

list_plotter(pal_data$color[ids], pal_data$names[ids], package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r rcartocolordiv, fig.height=8}
package_name <- "rcartocolor"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerdiv, fig.height=10}
package_name <- "RColorBrewer"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderdiv, fig.height=8}
package_name <- "Redmonder"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r scicodiv, fig.height=7}
package_name <- "scico"
pal_data <- all_names(package_name, "diverging")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("thomasp85/scico")
# CRAN version
install.packages("scico")
```

### Qualitative color palettes

```{r awtoolsqua, fig.height=6}
package_name <- "awtools"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("awhstin/awtools")
```

```{r cartographyqua, fig.height=3}
package_name <- "cartography"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("riatelab/cartography")
# CRAN version
install.packages("cartography")
```

```{r dichromatqua, fig.height=2.5}
package_name <- "dichromat"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("dichromat")
```

```{r dutchmastersqua, fig.height=7}
package_name <- "dutchmasters"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("EdwinTh/dutchmasters")
```

```{r ggsciqua, fig.height=23}
package_name <- "ggsci"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("road2stat/ggsci")
# CRAN version
install.packages("ggsci")
```

```{r ggthemesqua, fig.height=30}
package_name <- "ggthemes"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jrnold/ggthemes")
# CRAN version
install.packages("ggthemes")
```

```{r ggpomologicalqua, fig.height=3}
package_name <- "ggpomological"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("gadenbuie/ggpomological")
```

```{r ghibliqua, fig.height=28}
package_name <- "ghibli"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ewenme/ghibli")
# CRAN version
install.packages("ghibli")
```

```{r jcolors-discrete, fig.height=11}
package_name <- "jcolors"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jaredhuling/jcolors")
# CRAN version
install.packages("jcolors")
```

```{r LaCroixColoRqua, fig.height=22}
package_name <- "LaCroixColoR"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("johannesbjork/LaCroixColoR")
```

```{r NineteenEightyRqua, fig.height=13}
package_name <- "NineteenEightyR"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("m-clark/NineteenEightyR")
# CRAN version
install.packages("NineteenEightyR")
```

```{r nordqua, fig.height=12}
package_name <- "nord"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("jkaupp/nord")
# CRAN version
install.packages("nord")
```

```{r ochRequa, fig.height=17}
package_name <- "ochRe"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ropenscilabs/ochRe")
# CRAN version
install.packages("ochRe")
```

```{r palettetownqua, fig.height=11}
ids <- c(6, 17, 114, 137, 156, 191, 193, 283, 311, 318)
package_name <- "palettetown"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color[ids], pal_data$names[ids], package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("timcdlucas/palettetown")
# CRAN version
install.packages("palettetown")
```

```{r palsdiscretequa, fig.height=9}
package_name <- "pals"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("kwstat/pals")
# CRAN version
install.packages("pals")
```

```{r Polychromequa, fig.height=8}
package_name <- "Polychrome"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Polychrome")
```

```{r quickpalettequa, fig.height=17}
package_name <- "quickpalette"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("EmilHvitfeldt/quickpalette")
```

```{r rcartocolorqua, fig.height=7}
package_name <- "rcartocolor"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("Nowosad/rcartocolor")
# CRAN version
install.packages("rcartocolor")
```

```{r RColorBrewerqua, fig.height=9}
package_name <- "RColorBrewer"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("RColorBrewer")
```

```{r Redmonderqua, fig.height=25}
package_name <- "Redmonder"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# CRAN version
install.packages("Redmonder")
```

```{r RSkittleBrewerqua, fig.height=6}
package_name <- "RSkittleBrewer"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("alyssafrazee/RSkittleBrewer")
```

```{r wesandersonqua, fig.height=20}
package_name <- "wesanderson"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("karthik/wesanderson")
# CRAN version
install.packages("wesanderson")
```

```{r yarrrqua, fig.height=22}
package_name <- "yarrr"
pal_data <- all_names(package_name, "qualitative")

list_plotter(pal_data$color, pal_data$names, package_name)
```

```{r eval=FALSE, echo=TRUE}
# Developmental version
devtools::install_github("ndphillips/yarrr")
# CRAN version
install.packages("yarrr")
```