---
title: ""
---

<script language="JavaScript" SRC="display.js"></script>
<script language="JavaScript" SRC="data.js"></script>
<script src="https://cdn-tailwindcss.vercel.app/?plugins=forms,typography,aspect-ratio,line-clamp"></script>

```{css, echo=FALSE}
html {
  font-size: 16px;
}
.main-container {
  width: 100%;
  max-width: 100%;
}
.container-fluid {
  padding-right: 0px;
  padding-left: 0px;
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shufflecards)
library(shiny)
library(crosstalk)
library(ggplot2)
library(dplyr)

```

<div class="min-h-screen bg-gray-100">

```{r}
tags$nav(class="bg-gray-800 px-8 py-4",
  div(class="flex items-center flex-wrap max-w-6xl mx-auto",
    a(href="index.html", class="py-2 lg:px-2 mr-4 items-center",
      span(class="text-2xl text-white font-bold uppercase tracking-wide", "Palette Picker")
    ),
    div(class="w-full lg:inline-flex lg:flex-grow lg:w-auto",
        div(class="lg:inline-flex lg:flex-row lg:ml-auto lg:w-auto w-full lg:items-center items-start flex flex-col lg:h-auto",
            a(href="index.html", class="text-lg lg:inline-flex lg:w-auto w-full lg:px-4 py-2 rounded text-gray-200 items-center justify-center hover:bg-gray-900 hover:text-white",
              "Home"  
            ),
            a(href="discrete.html", class="text-lg lg:inline-flex lg:w-auto w-full lg:px-4 py-2 rounded text-gray-200 items-center justify-center hover:bg-gray-900 hover:text-white",
              "Discrete"  
            )
        )
    )
  )
)
```


<div class="max-w-6xl py-24 mx-auto prose">

# R Color Palettes

This is a new iteration of the [r-color-palettes](https://github.com/EmilHvitfeldt/r-color-palettes) repository.

This website is in early stages of development. Think alpha build. More functionality and information will be added.

Any feedback, suggestions, or styling help are welcome as [issues](https://github.com/EmilHvitfeldt/r-color-palettes/issues).

Styling of website was added by [Kyle F Butts](https://twitter.com/kylefbutts)

Available palette pickers:

- [Discrete Color Palettes](discrete.html)

</div>
</div>